A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2025-01-09 manuscript/main.tex
rm symbolic link manuscript/images

%\begin{figure}[H]
%       \centering
%       \begin{subfigure}{0.3\textwidth}
	%               \centering
	%               \includegraphics[width=\textwidth]{images/encoders/quantikz/A1.png}
	%               \caption{}
	%               \label{fig:A1}
	%       \end{subfigure}%
%       \hfill
%       \begin{subfigure}{0.3\textwidth}
	%               \centering
	%               \includegraphics[width=\textwidth]{images/encoders/quantikz/A2.png}
	%               \caption{}
	%               \label{fig:A2}
	%       \end{subfigure}%
%       \hfill
%       \begin{subfigure}{0.3\textwidth}
	%               \centering
	%               \includegraphics[width=1\textwidth]{images/encoders/quantikz/M.png}
	%               \caption{}
	%               \label{fig:M}
	%       \end{subfigure}%
%       \hfill
%       \begin{subfigure}{1\textwidth}
	%               \centering
	%                   \includegraphics[width=\textwidth]{images/encoders/quantikz/IQP.png}
	%               \caption{}
	%               \label{fig:IQP}
	%       \end{subfigure}%
%       \caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
%       \label{fig:encoders}
%\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/encoders/quantikz/combined.png}
	\caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
	\label{fig:encoders}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/ansatz/quantikz/combined.png}
	\caption{(a) Modified-Pauli-CRZ, (b) Modified-Pauli-CRX, (c) Efficient-CRZ, (d) Efficient-CRX, (e) HWE-CNOT, (f) HWE-CZ,  (g) ESU2, (h) Full-Pauli-CRZ, (i) Full-Pauli-CRX, (j) Hadamard, (k) Full-CRZ, and (l)Full-CRX}
	\label{fig:ansatz}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/linear_train_vs_test.png}
		\caption{}
		\label{fig:linear_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
		\caption{}
		\label{fig:quadratic_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/sine_train_vs_test.png}
		\caption{}
		\label{fig:sine_train_vs_test}
	\end{subfigure}
	\caption{}
	\label{fig:train_vs_test}
\end{figure}

@@

% Make distribution plot
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=\linewidth]{images/BSE.png}
%	\caption{BSE}
%	\label{fig:BSE}
%\end{figure}

@@

 \begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/BSE/classical_features_MAE.png}
		\caption{}
		\label{fig:BSE_bse_classical_features_MAE}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/BSE/classical_features_R2.png}
		\caption{}
		\label{fig:BSE_classical_features_R2}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/DDCC/DDCC_feature_set.png}
		\caption{}
		\label{fig:DDCC_feature_set}
	\end{subfigure}
	\hfill	
	\caption{}
	\label{fig:chemical_classical_features}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/linear_heatplots.png}
		\caption{}
		\label{fig:linear_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/linear_boxplots.png}
		\caption{}
		\label{fig:linear_boxplots}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/quadratic_heatplots.png}
		\caption{}
		\label{fig:quadratic_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/quadratic_boxplots.png}
		\caption{}
		\label{fig:quadratic_boxplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/sine_heatplots.png}
		\caption{}
		\label{fig:sine_heatplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/sine_boxplots.png}
		\caption{}
		\label{fig:sine_boxplots}
	\end{subfigure}
	\hfill		
	\caption{}
	\label{fig:fivequbit_ff_heat}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/linear_heatplots.png}
		\caption{}
		\label{fig:sixteenlinear_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/linear_boxplots.png}
		\caption{}
		\label{fig:sixteenlinear_boxplots}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/quadratic_heatplots.png}
		\caption{}
		\label{fig:sixteenquadratic_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/quadratic_boxplots.png}
		\caption{}
		\label{fig:sixteenquadratic_boxplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/sine_heatplots.png}
		\caption{}
		\label{fig:sixteensine_heatplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/sine_boxplots.png}
		\caption{}
		\label{fig:sixteensine_boxplots}
	\end{subfigure}
	\hfill		
	\caption{}
	\label{fig:sixteensixteenqubit_ff_heat}
\end{figure}

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
		\caption{}
		\label{fig:16qubit_Linear_RUD_AL}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/linear_circuitdepth_vs_R2}
		\caption{}
		\label{fig:linear_circuitdepth_vs_R2}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Quadratic_RUD_AL}
		\caption{}
		\label{fig:16qubit_Quadratic_RUD_AL}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/quadratic_circuitdepth_vs_R2}
		\caption{}
		\label{fig:quadratic_circuitdepth_vs_R2}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
		\caption{}
		\label{fig:16qubitlinearrudal}
	\end{subfigure}	
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sine_circuitdepth_vs_R2}
		\caption{}
		\label{fig:sine_circuitdepth_vs_R2}
	\end{subfigure}
	\hfill		
	\caption{}
	\label{fig:16qubit_RUD_AL}	
\end{figure}

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/linear_learning_curves.png}
		\caption{}
		\label{fig:linear_learning_curves}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/quadratic_learning_curves.png}
		\caption{}
		\label{fig:quadratic_learning_curves}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/Function_Fitting/sine_learning_curves.png}
		\caption{}
		\label{fig:sine_learning_curves}
	\end{subfigure}	
	\caption{}
	\label{fig:functionfitting_learning_curves}	
\end{figure}

@@

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/DDCC/DDCC_heatplots}
		\caption{}
		\label{fig:ddccheatplots}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/DDCC/DDCC_boxplots}
		\caption{}
		\label{fig:ddccboxplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
		\caption{}
		\label{fig:allddcc5circuitdepthr2vsiterationtime}
	\end{subfigure}	
	\caption{}
	\label{fig:ddcc_all_analysis}	
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/DDCC/DDCC_RUDAL}
	\caption{}
	\label{fig:ddccrudal}
\end{figure}

>>>>

%\begin{figure}[H]
%       \centering
%       \begin{subfigure}{0.3\textwidth}
	%               \centering
	%               \includegraphics[width=\textwidth]{../images/encoders/quantikz/A1.png}
	%               \caption{}
	%               \label{fig:A1}
	%       \end{subfigure}%
%       \hfill
%       \begin{subfigure}{0.3\textwidth}
	%               \centering
	%               \includegraphics[width=\textwidth]{../images/encoders/quantikz/A2.png}
	%               \caption{}
	%               \label{fig:A2}
	%       \end{subfigure}%
%       \hfill
%       \begin{subfigure}{0.3\textwidth}
	%               \centering
	%               \includegraphics[width=1\textwidth]{../images/encoders/quantikz/M.png}
	%               \caption{}
	%               \label{fig:M}
	%       \end{subfigure}%
%       \hfill
%       \begin{subfigure}{1\textwidth}
	%               \centering
	%                   \includegraphics[width=\textwidth]{../images/encoders/quantikz/IQP.png}
	%               \caption{}
	%               \label{fig:IQP}
	%       \end{subfigure}%
%       \caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
%       \label{fig:encoders}
%\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../images/encoders/quantikz/combined.png}
	\caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
	\label{fig:encoders}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{../images/ansatz/quantikz/combined.png}
	\caption{(a) Modified-Pauli-CRZ, (b) Modified-Pauli-CRX, (c) Efficient-CRZ, (d) Efficient-CRX, (e) HWE-CNOT, (f) HWE-CZ,  (g) ESU2, (h) Full-Pauli-CRZ, (i) Full-Pauli-CRX, (j) Hadamard, (k) Full-CRZ, and (l)Full-CRX}
	\label{fig:ansatz}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/linear_train_vs_test.png}
		\caption{}
		\label{fig:linear_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
		\caption{}
		\label{fig:quadratic_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/sine_train_vs_test.png}
		\caption{}
		\label{fig:sine_train_vs_test}
	\end{subfigure}
	\caption{}
	\label{fig:train_vs_test}
\end{figure}

@@

% Make distribution plot
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=\linewidth]{../images/BSE.png}
%	\caption{BSE}
%	\label{fig:BSE}
%\end{figure}

@@

 \begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/BSE/classical_features_MAE.png}
		\caption{}
		\label{fig:BSE_bse_classical_features_MAE}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/BSE/classical_features_R2.png}
		\caption{}
		\label{fig:BSE_classical_features_R2}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/DDCC/DDCC_feature_set.png}
		\caption{}
		\label{fig:DDCC_feature_set}
	\end{subfigure}
	\hfill	
	\caption{}
	\label{fig:chemical_classical_features}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/linear_heatplots.png}
		\caption{}
		\label{fig:linear_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/linear_boxplots.png}
		\caption{}
		\label{fig:linear_boxplots}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/quadratic_heatplots.png}
		\caption{}
		\label{fig:quadratic_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/quadratic_boxplots.png}
		\caption{}
		\label{fig:quadratic_boxplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/sine_heatplots.png}
		\caption{}
		\label{fig:sine_heatplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/sine_boxplots.png}
		\caption{}
		\label{fig:sine_boxplots}
	\end{subfigure}
	\hfill		
	\caption{}
	\label{fig:fivequbit_ff_heat}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/linear_heatplots.png}
		\caption{}
		\label{fig:sixteenlinear_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/linear_boxplots.png}
		\caption{}
		\label{fig:sixteenlinear_boxplots}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/quadratic_heatplots.png}
		\caption{}
		\label{fig:sixteenquadratic_heatplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/quadratic_boxplots.png}
		\caption{}
		\label{fig:sixteenquadratic_boxplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/sine_heatplots.png}
		\caption{}
		\label{fig:sixteensine_heatplots}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/sine_boxplots.png}
		\caption{}
		\label{fig:sixteensine_boxplots}
	\end{subfigure}
	\hfill		
	\caption{}
	\label{fig:sixteensixteenqubit_ff_heat}
\end{figure}

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
		\caption{}
		\label{fig:16qubit_Linear_RUD_AL}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_circuitdepth_vs_R2}
		\caption{}
		\label{fig:linear_circuitdepth_vs_R2}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Quadratic_RUD_AL}
		\caption{}
		\label{fig:16qubit_Quadratic_RUD_AL}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_circuitdepth_vs_R2}
		\caption{}
		\label{fig:quadratic_circuitdepth_vs_R2}
	\end{subfigure}
	\hfill		
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
		\caption{}
		\label{fig:16qubitlinearrudal}
	\end{subfigure}	
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_circuitdepth_vs_R2}
		\caption{}
		\label{fig:sine_circuitdepth_vs_R2}
	\end{subfigure}
	\hfill		
	\caption{}
	\label{fig:16qubit_RUD_AL}	
\end{figure}

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_learning_curves.png}
		\caption{}
		\label{fig:linear_learning_curves}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_learning_curves.png}
		\caption{}
		\label{fig:quadratic_learning_curves}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_learning_curves.png}
		\caption{}
		\label{fig:sine_learning_curves}
	\end{subfigure}	
	\caption{}
	\label{fig:functionfitting_learning_curves}	
\end{figure}

@@

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_heatplots}
		\caption{}
		\label{fig:ddccheatplots}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_boxplots}
		\caption{}
		\label{fig:ddccboxplots}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
		\caption{}
		\label{fig:allddcc5circuitdepthr2vsiterationtime}
	\end{subfigure}	
	\caption{}
	\label{fig:ddcc_all_analysis}	
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL}
	\caption{}
	\label{fig:ddccrudal}
\end{figure}
